%!TEX encoding = UTF-8 Unicode
%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
\cventry
  {Backend Engineer} % Job title
  {AO Labs} % Organization
  {Seoul, S.Korea} % Location
  {May. 2024 - Present} % Date(s)
  {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item[] {\textbf{Market service} \hspace{1cm} \textit{Go, Redis (Pubsub \& Stream), TimescaleDB (PostreSQL)}}
        \item {Designed and implemented a service that dynamically subscribes to and processes real-time market data, including token prices.}
        \item[] 
        \item[] {\textbf{Backend of a Blockchain-based Service} \hspace{1cm} \textit{Go, gRPC, GCP, Cloud Run, GCP Pubsub, MySQL}}
        \item {Subscribed to and indexed blockchain data.}
        \item {Developed an admin tool using low-code platform(Retool).}
      \end{cvitems}
  }

%---------------------------------------------------------
\cventry
  {Backend Engineer, Team Lead} % Job title
  {Mathpresso, Inc.} % Organization
  {Seoul, S.Korea} % Location
  {Jan. 2022 - May. 2024} % Date(s)
  {
    \begin{cvsubentries}
      \cvsubentry{}{\small \underline{Lab Development Team Lead}}{Oct. 2022 - Mar. 2023}{}
      \begin{cvitems}
        \item[] {Led a team of around 5 backend engineers, responsible for the QADNA service's problem search engine and data collection to indexing.}
        \item {Focused on maximizing individual strengths to improve team performance.}
        \begin{itemize}
          \item {Identified strengths and set career goals through regular one-on-one meetings.}
        \end{itemize}
        \item {Created an environment for fast and smooth communication to enhance team productivity.}
        \begin{itemize}
          \item {Streamlined meetings and fostered a positive atmosphere.}
        \end{itemize}
        \item[]
      \end{cvitems}
      \cvsubentry{}{\small \underline{Content Platform TF Lead}}{Mar. 2023 - May. 2024}{}
      \begin{cvitems}
        \item[] {Managed a team of about 7 members, including engineers, domain experts, and service operators, aiming to efficiently create and manage large volumes of high-quality problem/solution data.}
        \item {Communicated with various stakeholders and participated in business decision-making.}
        \item {Supported the team in sharing common goals while utilizing resources for different missions.}
        \begin{itemize}
          \item {Established quantitative key performance indicators.}
          \item {Presented expected outcomes based on goal achievement.}
        \end{itemize}
        \item[] 
      \end{cvitems}
    \end{cvsubentries}
  }

%---------------------------------------------------------
\cventry
  {} % Job title
  {} % Organization
  {} % Location
  {} % Date(s)
  {
  \begin{cvsubentries}
    \cvsubentry{}{\small \underline{Backend Engineer}}{Jan. 2022 - May. 2024}{}
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item[] {\textbf{Knowledge Graph} \hspace{1cm} \textit{Go, Neo4j (graphDB)}}
      \item[] {Project to flexibly manage relationships between key models in math education (e.g., problem types, concepts, prerequisite and subsequent concepts).}
      \item {Participated from the planning phase to systematize from conceptual units to curriculum, utilizing concept-based data such as problem labeling.}
      \item[] 
      \item[] {\textbf{Data Pipeline} \hspace{1cm} \textit{Go, MySQL, GCP, AppEngine}}
      \item {Developed data collection, processing, and pipelines for search engines, AI learning, and content services.}
      \item[] 
      \item[] {\textbf{Problem/Solution Resource Service} \hspace{1cm} \textit{Go, MySQL, Neo4j}}
      \item {Managed and optimized problem/solution data.}
      \item[] 
      \item[] {\textbf{Image Search} \hspace{1cm} \textit{Go, Milvus (Vector DB)}}
      \item {Built an image search service by integrating in-house Image Embedding models with vector databases.}
      \item[]
    \end{cvitems}
  \end{cvsubentries}
  }

%---------------------------------------------------------
  \cventry
    {Backend Engineer} % Job title
    {Kasa Korea Co., Ltd.} % Organization
    {Seoul, S.Korea} % Location
    {Jul. 2019 - Sep. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item[] {\textbf{Kasa Service Web Server.} \hspace{1cm} \textit{Django, DRF, MySQL, redis}}
        \item {Contributed project from scratch and experienced in early stages of operation.}
        \item {Implemented Authentication, Public Offering, Ledger services. Designed entity-relation and REST API.}
        \item[]
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Backend Engineer} % Job title
    {Omnious. Co., Ltd.} % Organization
    {Seoul, S.Korea} % Location
    {Nov. 2017 - Jul. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item[] {\textbf{Labeling Tool}}
        \item {Maintained backend of in-house web application having 50+ active users for collecting fashion data to train AI model.}
        \begin{itemize}
          \item[] \textit{Docker, CircleCI, Rancher, AWS(EC2, S3, RDS)}
        \end{itemize}
        \item {Designed RESTful HTTP API, developed server serving them. Documented API specification for communication.}
        \begin{itemize}
          \item[] \textit{flask, NGINX, uWSGI, Swagger}
        \end{itemize}
        \item {Established relation of domain model, designed database schema.}
        \begin{itemize}
          \item[] \textit{MySQL}
        \end{itemize}
        \item {Built HTTP access logging system and pipeline to store it.}
        \begin{itemize}
          \item[] \textit{fluntd, fluent-bit}
        \end{itemize}
        \item {Introduced unit testing, style guide of codebase.}
        \begin{itemize}
          \item[] \textit{flake8, pytest}
        \end{itemize}
        \item[]
        \item[] {\textbf{Data Extraction \& Transformation} \hspace{1cm} \textit{pandas, Celery}}
        \item {Extracted collected data to train AI model and pre-processed in a form that is easy to train.}
        \item {Automated process from data extraction to data processing, developed CLI tool to access automated data transfer system.}
        \item[]
        \item[] {\textbf{Crawler} \hspace{1cm} \textit{Scrapy, ScrapingHub, Zappa, AWS(SNS, SQS, Labmda)}}
        \item {Implemented 20+ web crawlers for collecting fashion images, developed a scheduling tool for management.} 
        \item {Built serverless pipeline that stores crawled data in a storage.}
        \item[]
      \end{cvitems}
    }

% %---------------------------------------------------------
%   \cventry
%     {Software Developer Intern} % Job title
%     {LayGen Inc.} % Organization
%     {Gyeonggi-do, S.Korea} % Location
%     {Aug. 2017 - Sep. 2017} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Participated to manufactoring operating module for a prototype of 3D printer and developed software control the module.}
%         \item {Developed GUI so that hardware engineer can test controling each part of 3D printer.}
%         \begin{itemize}
%           \item[--] \textit{Python, PyQT, Rasberry Pi, Arduino}
%         \end{itemize}
%       \end{cvitems}
%     }

%---------------------------------------------------------
  \cventry
    {Software Developer Intern} % Job title
    {LINE Corp.} % Organization
    {Gyeonggi-do, S.Korea, S.Korea} % Location
    {Apr. 2017 - May. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item[] {\textbf{Targeted Video} \hspace{1cm} \textit{Swift, OpenCV}}
        \item[] {Developed an iOS app for isolating and modifying desired objects in videos.}
        \item {Used technique of contour extraction, image segmentation and stabilization.}
        \item {Implemented video editing function that cuts or pastes object user selected.}
      \end{cvitems}
    }

%---------------------------------------------------------
  % \cventry
  %   {Software Developer Intern} % Job title
  %   {UXEnterprise} % Organization
  %   {Seoul, S.Korea} % Location
  %   {Aug. 2016 - Sep. 2016} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Prototyped Android application viewing Female biorhythm.}
  %       \item {Implemented connection with a measuring device using Bluetooth.}
  %       \item[--] \textit{Java, Android}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------
\end{cventries}
